### 2013-02-15 doc/icml2013/regression.tex
More fixes

Our analysis is based on the low-rank regression framework of
\citet{Tomioka2011} for tensors, which builds off of
\citet{NegahbanWainwright2009} for matrices.
The main challenge is to control the noise $\eta_p(x)$,
which in addition to containing the usual Gaussian part, is also dependent on
$x$, involves the mixing noise and various cross terms.
We first set up some notation to all three regressions (\refeqn{estimateM1}, \refeqn{estimateM2}, and \refeqn{estimateM3}).
Define the observation operator $\opX_p(M_p) : \Re^{d\tp{p}} \to \Re^{n}$
mapping compound parameters $M_p$:
\begin{align}
\opX_p(M_p; \sD)_i &\eqdef \frac12 \sum_{(x,y) \in \sD} \innerp{M_p}{x\tp{p}}_i, \quad i  \in [n].
\end{align}

Let $\kappa(\opX_p)$ be the restricted strong constant,
and let $\opX^*_p(\eta_p; \sD) = \sum_{(x,y) \in \sD} \eta_p(x) x\tp{p}$
be the adjoint.

>>>>

Our analysis is based on the low-rank regression framework of
\citet{Tomioka2011} for tensors, which builds off of
\citet{NegahbanWainwright2009} for matrices.
The main challenge is to control the noise $\eta_p(x)$,
which in addition to containing the usual Gaussian part, is also dependent on
$x$, involves the mixing noise and various cross terms.
We first set up some notation that unifies all three regressions (\refeqn{estimateM1}, \refeqn{estimateM2}, and \refeqn{estimateM3}).
Define the observation operator $\opX_p(M_p) : \Re^{d\tp{p}} \to \Re^{n}$
mapping compound parameters $M_p$:
\begin{align}
\opX_p(M_p; \sD)_i &\eqdef \frac12 \sum_{(x,y) \in \sD} \innerp{M_p}{x\tp{p}}_i, \quad i  \in [n].
\end{align}

Let $\kappa(\opX_p)$ be the restricted strong convexity constant,
and let $\opX^*_p(\eta_p; \sD) = \sum_{(x,y) \in \sD} \eta_p(x) x\tp{p}$
be the adjoint.
